Restructuring Data for Exascale Scientific Productivity

### 2016-04-09 papers/2016-Supercomputing/paper.tex
added a first pass at the storage hierarchy section.
Copied the quality of service section directly from the HotStorage paper as a
placeholder. This may move elsewhere in the paper and definitely needs to be
edited to avoid a plagarism issue.

\numberofauthors{1}
\author{
  \alignauthor {
    Jay Lofstead\footnotemark[1]~~,
    Hasan Abbasi\footnotemark[3]~~,
    Mark Ainsworth\footnotemark[6]~\footnotemark[3]~~,
    Jong Choi\footnotemark[3]~~,
    Matthew Curry\footnotemark[1]~~,\\
    Scott Klasky\footnotemark[3]~\footnotemark[4]~\footnotemark[7]~~,
    Tahsin Kurc\footnotemark[9]~~,
    Qing Liu\footnotemark[3]~~,
    Jeremy Logan\footnotemark[4]~~,
    Carlos Maltzahn\footnotemark[2]~~,
    Manish Parashar\footnotemark[5]~~,\\
    Norbert Podhorzski\footnotemark[3]~~,
    Feiyi Wang\footnotemark[3]~~,
    Matthew Wolf\footnotemark[7]~~,
    Ben Whitney\footnotemark[6]~~,
    C. S. Chang\footnotemark[8]~~,
    Michael Churchill\footnotemark[8]~~,
    Stephane Ethier\footnotemark[8]~~
  }\\
  \footnotemark[1]~~Sandia National Laboratories,
  \footnotemark[2]~~University of California Santa Cruz,\\
  \footnotemark[3]~~Oak Ridge National Laboratory,
  \footnotemark[4]~~U. Tenn. Knoxville,
  \footnotemark[5]~~Rutgers University,\\
  \footnotemark[6]~~Brown University,
  \footnotemark[7]~~Georgia Tech,
  \footnotemark[8]~~PPPL,
  \footnotemark[9]~~Stony Brook
}
\maketitle

@@

Responsibilities:
\begin{itemize}
\item Jay - write draft/drive paper
\item everyone - experiment runs
\item Ivan - DataSpaces help
\item Tahsin/Jong - Use real XGC1 data in test harness
\item Tahsin/Jong - Big run for byte split example
\item Tahsin/Jong - small run for interpolation example
\item Hadan - Real S3D run
\item Hasan/Norbert - ADIOS writer
\item James/Dave - ADIOS reader/viz
\item Hasan/Ben - ADIOS interpolation pieces
\end{itemize}

>>>>

\numberofauthors{1}
\author{
  \alignauthor {
    Hasan Abbasi\footnotemark[3]~~,
    Jay Lofstead\footnotemark[1]~~,
    Mark Ainsworth\footnotemark[6]~\footnotemark[3]~~,
    Jong Choi\footnotemark[3]~~,
    Matthew Curry\footnotemark[1]~~,\\
    Scott Klasky\footnotemark[3]~\footnotemark[4]~\footnotemark[7]~~,
    Tahsin Kurc\footnotemark[9]~~,
    Qing Liu\footnotemark[3]~~,
    Jeremy Logan\footnotemark[4]~~,
    Carlos Maltzahn\footnotemark[2]~~,
    Manish Parashar\footnotemark[5]~~,\\
    Norbert Podhorzski\footnotemark[3]~~,
    Feiyi Wang\footnotemark[3]~~,
    Matthew Wolf\footnotemark[7]~~,
    Ben Whitney\footnotemark[6]~~,
    C. S. Chang\footnotemark[8]~~,
    Michael Churchill\footnotemark[8]~~,
    Stephane Ethier\footnotemark[8]~~
  }\\
  \footnotemark[1]~~Sandia National Laboratories,
  \footnotemark[2]~~University of California Santa Cruz,\\
  \footnotemark[3]~~Oak Ridge National Laboratory,
  \footnotemark[4]~~U. Tenn. Knoxville,
  \footnotemark[5]~~Rutgers University,\\
  \footnotemark[6]~~Brown University,
  \footnotemark[7]~~Georgia Tech,
  \footnotemark[8]~~PPPL,
  \footnotemark[9]~~Stony Brook
}
\maketitle

@@

Responsibilities:
\begin{itemize}
\item Hasan - write draft/drive paper
\item everyone - experiment runs
\item Ivan - DataSpaces help
\item Tahsin/Jong - Use real XGC1 data in test harness
\item Tahsin/Jong - Big run for byte split example
\item Tahsin/Jong - small run for interpolation example
\item Hasan - Real S3D run
\item Hasan/Norbert - ADIOS writer
\item James/Dave - ADIOS reader/viz
\item Hasan/Ben - ADIOS interpolation pieces
\item Jay/Carlos - Storage hierarchy information
\end{itemize}
